# Automated Class Functions

## Preliminary Notes

The stuff below works on the College's R Studio Server (CentOS 7 operating system).

In previous versions the user had to create a password file.  This is no longer the case:  now all you need is membership in the `wheel` and `instructor` groups.  The MAT 111 Czar will take care of this for you (though you may need to remind him/her to do this).

This version of the scripts is tailored to the current RStudio server, in which all regular users are in the `/home/GEORGETOWNCOLLEGE.EDU` directory.

## Installation and Setup

A convenient way to obtain the scripts is through git.

```{r eval = FALSE}
git clone https://github.com/homerhanumat/itr.git
```

### Install for the First Time

Save copies of `collecthomework.pl`, `createdirectories.pl` and `returnhomework.pl` into your Home directory on the Server.  (They are in the `perl` directory.)  Also save a copy of `class_functions.Rmd` to your Home.  **Never modify the contents of `itr`!**  (If you do, there will be problems updating later on.)

### Updates

To update the scripts, go to the Shell and run:

```{r eval = F}
cd itr
git pull origin master
```

Then repeat the saving process.

### Setup

Create a textfile of student usernames, one per line in the usual way, and save it to your Home directory.  In the examples that follow, this file will be called `students.txt`.

Create a directory in your Home directory called `homework`.

## Directory Creation

To create directories, use the script `creatdirectories.pl`.  Click on the Terminal tab and copy the following into the Terminal at the prompt:

```{sh eval = FALSE}
sudo perl createdirectories.pl --studentfile=special.txt
```

Then press Enter, give your password when requested, and watch it go.

## Homework Collection

To collect homework run something like this in the Terminal:

```{sh eval = F}
sudo perl collecthomework.pl --inst=hwhite0 --assign=MAT331_Final --file=students_331.txt
```

**Note:**  modify the `inst`, `assign` and `file` arguments as needed!

## Returning Homework

Run something like this in the terminal:


```{sh eval = FALSE}
sudo perl returnhomework.pl --path=MAT331_Final --inst=hwhite0 --file=students_331.txt --flag=_com
```

Again, modify arguments as needed.  In this script:

* `path` is the tag you used to identify an assignment to collect (it's the `assign` tag from `collecthomework.pl` script);
* `flag` is the tag you include in the filename of the "comments" version that you plan to return to students.


## Generating a Report

(**Note**:  In the era of attendance-taking on GConnect we don't use this feature.)

For this you will use still use **classr** as described in the package vignette, i.e., something like:

```{r eval = FALSE}
myReport <- SubmissionReport(studentfile="students.txt",
                             folder="homework",
                             assigntype="DA")
```