# Automated Class Functions

## Preliminary Notes

The stuff below works on my Debian system running Perl version 5.20.  Note that in the new scripts the group is "instructors", not "admins".

You no longer need to create a password file:  all you need are admin privileges.

This version of the scripts works when you the students are all directoy under the `/home` directory (not in, for instance `/home/FAST`.  Also it works best if you have just one class at a time.  I'll fix this in later versions, as needed.)

## Directory Creation

To create directories, use the script `creatdirectories.pl` in your Home directory.  Open the shell (**Tools --> Shell**) and run:

```{sh eval = FALSE}
sudo perl createdirectories.pl --studentfile=students.txt
```

## Homework Collection

To collect homework,  just modify the command below and run it from within R:

```{r eval = FALSE}
system("perl collecthomework.pl --instructor=homer --assignment=HW02 --studentfile=students.txt")
```

No `sudo` is required here.

## Returning Homework

Put the script `returnhomework.pl` into your Home directory.  Open it and modify the following parameters:

* `$instructor`
* `$studentfile`
* `$flag`

Open the shell (**Tools --> Shell** ) and run something like this:


```{sh eval = FALSE}
sudo perl returnhomework.pl --path=HW02
```

## Generating a Report

For this you will use classr, as described in the package vignette, i.e., something like:

```{r eval = FALSE}
myReport <- SubmissionReport(studentfile="students.txt",
                             folder="homework",
                             assigntype="DA")
```



