# Automated Class Functions

## Preliminary Notes

The stuff below works on my Debian system running Perl version 5.20, and on the College server running Ubuntu 14.04 and Perl 5.18.

In previous versions the user had to create a password file.  This is no longer the case:  now all you need is membership in the `sudo` and `instructor` groups.  The MAT 111 Czar will take care of this for you (though you may need to remind him/her to do this).

This version of the scripts is tailored to the current RStudio server, in which all regular users are in the `/home/FAST` directory.

## Installation and Setup

A conveneint way to obtain the scipts is through git.

```{r eval = FALSE}
git clone https://github.com/homerhanumat/itr.git
```


Save copies of `collecthomework.pl`, `createdirectories.pl` and `returnhomework.pl` into your Home directory on the Server.

To update:

```{r eval = F}
cd itr
git pull origin master
```


Create a textfile of student usernames, one per line in the usual way, and save it to your Home directory.  In the examples that follow, this file will be called `students.txt`.

Create a directory in your Home directory called `homework`.

## Directory Creation

To create directories, use the script `creatdirectories.pl`.  Open the shell (**Tools --> Shell**) and run:

```{sh eval = FALSE}
sudo perl createdirectories.pl --studentfile=students.txt
```

## Homework Collection

To collect homework,  just modify the command below and run it from within R:

```{r eval = FALSE}
system("perl collecthomework.pl --inst=hwhite0 --assign=HW02 --file=students.txt")
```

No `sudo` is required here.  **Note:**  modify the `inst`, `assign` and `file` arguments as needed!

## Returning Homework

Open the shell (**Tools --> Shell** ) and run something like this:


```{sh eval = FALSE}
sudo perl returnhomework.pl --path=HW02 --inst=hwhite0 --file=students.txt --flag=_com
```

Again, modify arguments as needed.  In this script:

* `path` is the tag you used to identify an assignment to collect (it's the `assign` tag from `collecthomework.pl` script);
* `flag` is the tag you include in the filename of the "comments" version that you plan to return to students.

## Generating a Report

For this you will use still use classr as described in the package vignette, i.e., something like:

```{r eval = FALSE}
myReport <- SubmissionReport(studentfile="students.txt",
                             folder="homework",
                             assigntype="DA")
```



